### 2016-11-08 paper1.tex
Added short captions for tables
Added all TOC elements
Fixed page numbering
Fixed fancy header for chapters and abstracts
Shuffled and resized figures

\begin{abstract}
We present a new stellar feedback model that reproduces superbubbles.
Superbubbles from clustered young stars evolve quite differently to individual
supernovae and are substantially more efficient at generating gas motions.  The
essential new components of the model are thermal conduction, sub-grid
evaporation and a sub-grid multi-phase treatment for cases where the simulation
mass resolution is insufficient to model the early stages of the superbubble.
The multi-phase stage is short compared to superbubble lifetimes.  Thermal
conduction physically regulates the hot gas mass without requiring a free
parameter.  Accurately following the hot component naturally avoids overcooling.
Prior approaches tend to heat too much mass, leaving the hot ISM below $10^6$ K
and susceptible to rapid cooling unless ad-hoc fixes were used.  The hot
phase also allows feedback energy to correctly accumulate from multiple,
clustered sources, including stellar winds and supernovae.

@@

\begin{figure*}
    \includegraphics[width=\textwidth]{figures1/onestar_homogeneous.eps}
    \caption[Feedback effects as a function of resolution]{Feedback effects as a
    function of resolution.  The above figure shows on the left the total radial
    momentum imparted to the medium, and on the right the total amount of mass
    heated to above $10^5\;\mathrm{K}$.  The red curves are the direct injection
    results, the blue corresponds to the simple feedback, while the green shows
    the results of the superbubble model.  Solid lines show the values from
    simulations run with resolutions of $128^3$ particles, dashed for $64^3$,
    and dotted for $32^3$.  Note that for the $32^3$ run, the simple model
    produces $\sim 2\times 10^5\;M_\odot$ of hot gas.}
    \label{onestar_homogeneous}
\end{figure*}

@@

\begin{figure}
    \includegraphics[width=\textwidth]{figures1/onestar_hottemp.eps}
    \caption[Peak temperature of feedback-heated gas in a superbubble]{Peak
    temperature of feedback-heated gas inside the isolated star cluster's hot
    bubble.  Evaporation quickly enters the self-regulating regime, and the
    temperature is roughly constant for the last $15\;\mathrm{Myr}$ of
    feedback.}
    \label{onestar_hottemp}
\end{figure}

@@

\begin{figure}
    \includegraphics[width=\textwidth]{figures1/onestar_kappa.eps}
    \caption[Dependence of superbubble heated gas on conduction coefficient]{Hot
    mass production as a function of the conduction coefficient $\kappa_0$.  As
    this figure shows, reducing $\kappa_0$ by a factor of 100 reduces the amount
    of hot mass generated through conduction by only a factor of $\sim2$. All
    $\kappa_0$ values have units of $\mathrm{erg\; s^{-1} K^{-7/2} cm^{-1}}$.}
    \label{onestar_kappa}
\end{figure}

@@

\begin{figure*}
    \includegraphics[width=\textwidth]{figures1/onestar_clumpy.eps}
    \caption[Feedback effects as a function of ISM homogeneity]{Feedback effects
    as a function of ISM homogeneity.  The above figure shows on the left the
    total radial momentum imparted to the medium, and on the right the total
    amount of mass heated to above $10^5\;\mathrm{K}$.  The red curves are the
    direct injection results, the blue corresponds to the simple feedback, while
    the green shows the results of the superbubble model.  Solid curves show the
    results for a homogeneous ISM, dashed for a single dense clump, and dotted
    for 6 dense clumps.}
    \label{onestar_clumpy}
\end{figure*}

@@

\begin{figure*}
    \includegraphics[width=\textwidth]{figures1/milkyway_column.eps}
    \caption[Column density and temperature images of isolated Milky Way]{Column
    Density (upper row) and temperature for the Milky Way simulation at
    $300\;\mathrm{Myr}$.  The vectors show the in-plane velocity.  Temperatures
    shown are averages between the two phases for multiphase particles.  Black
    points in the face-on images show stars formed within the last
    $20\;\mathrm{Myr}$. Note that gas is both leaving the disc near the galactic
    core, and returning in some places near the edge.}
    \label{milkyway_column}
\end{figure*}

\begin{figure*}
    \includegraphics[width=\textwidth]{figures1/milkyway_outflow.eps}
    \caption[Outflow evolution in isolated Milky Way]{Outflow evolution for the
    Milky Way-like simulation.  The left hand plot shows the star formation rate
    and the outflow rate The right hand plot shows the average outflow
    velocity.}
    \label{milkyway_outflow}
\end{figure*}

@@

\subsection{Galaxy Simulations}\label{galaxy}
\subsubsection{Initial Conditions and Parameters}
We used the isolated disc galaxy initial condition from the AGORA comparison
project \citep{Kim2013}.  These initial conditions were generated using the
equilibrium disc generating code of \citet{Springel2005}.
This galaxy is similar to a MW-type spiral galaxy
at $z=0$.  For our dwarf simulation, we scaled the masses down by a factor of
100, and the length scales by a factor of $100^{1/3}$, preserving the physical
densities in the initial conditions and lowering the surface density.  The dwarf
is thus similar to a low surface density local dwarf spiral.  These initial
conditions were intended to be similar to the $G10$ and $G12$ initial conditions
used in \citet{DallaVecchia2012}. The properties of these initial conditions are
shown in table 1.  Both simulations have 312500 total particles and 100000 gas
particles, so that the mass resolution is substantially higher in the dwarf.  The
initial gas metallicity is solar in both cases.

We also simulated these initial conditions using the established `blastwave'
feedback model from \citep{Stinson2006}, which has been a standard feedback
model for galaxy simulations in numerous previous studies.
\begin{table}
    \begin{tabular}{ c c c c c}
        \hline
        Simulation & $M_{tot} \mathrm{(M_\odot)}$ & $M_{gas} \mathrm{(M_\odot)}$
        & $\epsilon \mathrm{(pc)}$ & $n_{SF} \mathrm{cm^{-3}}$\\
        \hline
        Milky Way & $1.3\times10^{12}$ & $8.6\times10^9$ & 20  & $>10$\\
        Dwarf & $1.3\times10^{10}$ &  $8.6\times10^7$ & 4.3 & $>50$\\
    \end{tabular}
    \caption{Disc galaxy initial conditions.  $\epsilon$ is the gravitational
    softening and $n_{SF}$ is the star formation threshold.}
\end{table}

\subsubsection{ISM properties and Star Formation Rates}\label{ISM}

@@

\begin{figure}
    \includegraphics[width=\textwidth]{figures1/kennicutt_schmidt.eps}
    \caption[Kennicutt-Schmidt law for isolated galaxies]{Kennicutt-Schmidt law
    in the Milky Way-like (blue points) and dwarf (red triangles) galaxies at
    $500\;\mathrm{Myr}$. Surface densities were calculated in radial annuli.
    The dashed line shows the Kennicutt-Schmidt Law.  The superbubble model is
    easily able to regulate star formation rates to within this range.}
    \label{kennicutt_schmidt}
\end{figure}

\begin{figure}
    \includegraphics[width=\textwidth]{figures1/multiphase_properties.eps}
    \caption[Properties of multiphase particles]{Properties of multiphase
    particles in the galaxy simulations.  The top figure shows duration of
    multiphase state for particles in both galaxy simulations.  Particles that
    are in the multiphase state more than once (convert back to single phase,
    cool, and then receive feedback again) have each time they are multiphase
    counted separately. The bottom figure shows maximum heights reached by
    particles in the multiphase state.  For each particle that is ever in the
    multiphase state, the maximum height it reaches {\it while still multiphase}
    is shown above for both galaxy simulations.  Dashed lines show scale heights
    at $10^4\;\mathrm{K}$ for each of the two simulations.}
    \label{multiphase_properties}
\end{figure}

@@

In order to compare superbubble feedback to \citet{DallaVecchia2012}, we selected
similar galaxies to the ones shown in their paper and calculated the properties
of their outflows using a similar method.  We adopt their two primary metrics,
mass outflow rate $\dot M$ and mean outflow velocity $<v_{\rm out}>$.  These two
metrics give us an idea as to both how much gas is ejected from the galaxies,
and how long that gas will take to return to the disc from the halo (if it does
return at all).

@@

\section*{Acknowledgements}
The analysis was performed using the pynbody package
(\texttt{https://github.com/pynbody/pynbody}, \citep{pynbody})
  We thank Mordecai-Mark Mac Low for useful
conversations regarding this paper.  The simulations were performed on the
clusters hosted on {\sc sharcnet}, part of ComputeCanada.  We greatly
appreciate the contributions of these computing allocations. James Wadsley and
Hugh Couchman thank NSERC for funding support.
\bibliographystyle{mnras}
\bibliography{library}

>>>>

\setcounter{pageFix}{\value{page}}
\begin{abstract}
\thispagestyle{fancy}
    \setcounter{page}{\value{pageFix}}
        \addcontentsline{toc}{section}{Abstract}
We present a new stellar feedback model that reproduces superbubbles.
Superbubbles from clustered young stars evolve quite differently to individual
supernovae and are substantially more efficient at generating gas motions.  The
essential new components of the model are thermal conduction, sub-grid
evaporation and a sub-grid multi-phase treatment for cases where the simulation
mass resolution is insufficient to model the early stages of the superbubble.
The multi-phase stage is short compared to superbubble lifetimes.  Thermal
conduction physically regulates the hot gas mass without requiring a free
parameter.  Accurately following the hot component naturally avoids overcooling.
Prior approaches tend to heat too much mass, leaving the hot ISM below $10^6$ K
and susceptible to rapid cooling unless ad-hoc fixes were used.  The hot
phase also allows feedback energy to correctly accumulate from multiple,
clustered sources, including stellar winds and supernovae.

@@

\begin{figure*}
    \includegraphics[width=0.8\textwidth]{figures1/onestar_homogeneous.eps}
    \caption[Feedback effects as a function of resolution]{Feedback effects as a
    function of resolution.  The above figure shows on the left the total radial
    momentum imparted to the medium, and on the right the total amount of mass
    heated to above $10^5\;\mathrm{K}$.  The red curves are the direct injection
    results, the blue corresponds to the simple feedback, while the green shows
    the results of the superbubble model.  Solid lines show the values from
    simulations run with resolutions of $128^3$ particles, dashed for $64^3$,
    and dotted for $32^3$.  Note that for the $32^3$ run, the simple model
    produces $\sim 2\times 10^5\;M_\odot$ of hot gas.}
    \label{onestar_homogeneous}
\end{figure*}

@@

\begin{figure}
    \includegraphics[width=0.5\textwidth]{figures1/onestar_hottemp.eps}
    \caption[Peak temperature of feedback-heated gas in a superbubble]{Peak
    temperature of feedback-heated gas inside the isolated star cluster's hot
    bubble.  Evaporation quickly enters the self-regulating regime, and the
    temperature is roughly constant for the last $15\;\mathrm{Myr}$ of
    feedback.}
    \label{onestar_hottemp}
\end{figure}

@@

\begin{figure}
    \includegraphics[width=0.6\textwidth]{figures1/onestar_kappa.eps}
    \caption[Dependence of superbubble heated gas on conduction coefficient]{Hot
    mass production as a function of the conduction coefficient $\kappa_0$.  As
    this figure shows, reducing $\kappa_0$ by a factor of 100 reduces the amount
    of hot mass generated through conduction by only a factor of $\sim2$. All
    $\kappa_0$ values have units of $\mathrm{erg\; s^{-1} K^{-7/2} cm^{-1}}$.}
    \label{onestar_kappa}
\end{figure}

@@

\begin{figure*}
    \includegraphics[width=0.8\textwidth]{figures1/onestar_clumpy.eps}
    \caption[Feedback effects as a function of ISM homogeneity]{Feedback effects
    as a function of ISM homogeneity.  The above figure shows on the left the
    total radial momentum imparted to the medium, and on the right the total
    amount of mass heated to above $10^5\;\mathrm{K}$.  The red curves are the
    direct injection results, the blue corresponds to the simple feedback, while
    the green shows the results of the superbubble model.  Solid curves show the
    results for a homogeneous ISM, dashed for a single dense clump, and dotted
    for 6 dense clumps.}
    \label{onestar_clumpy}
\end{figure*}

@@

\subsection{Galaxy Simulations}\label{galaxy}
\subsubsection{Initial Conditions and Parameters}
\begin{figure*}
    \includegraphics[width=\textwidth]{figures1/milkyway_column.eps}
    \caption[Column density and temperature images of isolated Milky Way]{Column
    Density (upper row) and temperature for the Milky Way simulation at
    $300\;\mathrm{Myr}$.  The vectors show the in-plane velocity.  Temperatures
    shown are averages between the two phases for multiphase particles.  Black
    points in the face-on images show stars formed within the last
    $20\;\mathrm{Myr}$. Note that gas is both leaving the disc near the galactic
    core, and returning in some places near the edge.}
    \label{milkyway_column}
\end{figure*}

We used the isolated disc galaxy initial condition from the AGORA comparison
project \citep{Kim2013}.  These initial conditions were generated using the
equilibrium disc generating code of \citet{Springel2005}.
This galaxy is similar to a MW-type spiral galaxy
at $z=0$.  For our dwarf simulation, we scaled the masses down by a factor of
100, and the length scales by a factor of $100^{1/3}$, preserving the physical
densities in the initial conditions and lowering the surface density.  The dwarf
is thus similar to a low surface density local dwarf spiral.  These initial
conditions were intended to be similar to the $G10$ and $G12$ initial conditions
used in \citet{DallaVecchia2012}. The properties of these initial conditions are
shown in table 1.  Both simulations have 312500 total particles and 100000 gas
particles, so that the mass resolution is substantially higher in the dwarf.  The
initial gas metallicity is solar in both cases.

We also simulated these initial conditions using the established `blastwave'
feedback model from \citep{Stinson2006}, which has been a standard feedback
model for galaxy simulations in numerous previous studies.
\begin{table}
    \begin{tabular}{ c c c c c}
        \hline
        Simulation & $M_{tot} \mathrm{(M_\odot)}$ & $M_{gas} \mathrm{(M_\odot)}$
        & $\epsilon \mathrm{(pc)}$ & $n_{SF} \mathrm{cm^{-3}}$\\
        \hline
        Milky Way & $1.3\times10^{12}$ & $8.6\times10^9$ & 20  & $>10$\\
        Dwarf & $1.3\times10^{10}$ &  $8.6\times10^7$ & 4.3 & $>50$\\
    \end{tabular}
    \caption[Isolated Disc Initial Conditions]{Disc galaxy initial conditions.  $\epsilon$ is the gravitational
    softening and $n_{SF}$ is the star formation threshold.}
\end{table}

\subsubsection{ISM properties and Star Formation Rates}\label{ISM}
\begin{figure*}
    \includegraphics[width=\textwidth]{figures1/milkyway_outflow.eps}
    \caption[Outflow evolution in isolated Milky Way]{Outflow evolution for the
    Milky Way-like simulation.  The left hand plot shows the star formation rate
    and the outflow rate The right hand plot shows the average outflow
    velocity.}
    \label{milkyway_outflow}
\end{figure*}

@@

@@

@@

\begin{figure}
    \includegraphics[width=0.6\textwidth]{figures1/kennicutt_schmidt.eps}
    \caption[Kennicutt-Schmidt law for isolated galaxies]{Kennicutt-Schmidt law
    in the Milky Way-like (blue points) and dwarf (red triangles) galaxies at
    $500\;\mathrm{Myr}$. Surface densities were calculated in radial annuli.
    The dashed line shows the Kennicutt-Schmidt Law.  The superbubble model is
    easily able to regulate star formation rates to within this range.}
    \label{kennicutt_schmidt}
\end{figure}

\begin{figure}
    \includegraphics[width=0.6\textwidth]{figures1/multiphase_properties.eps}
    \caption[Properties of multiphase particles]{Properties of multiphase
    particles in the galaxy simulations.  The top figure shows duration of
    multiphase state for particles in both galaxy simulations.  Particles that
    are in the multiphase state more than once (convert back to single phase,
    cool, and then receive feedback again) have each time they are multiphase
    counted separately. The bottom figure shows maximum heights reached by
    particles in the multiphase state.  For each particle that is ever in the
    multiphase state, the maximum height it reaches {\it while still multiphase}
    is shown above for both galaxy simulations.  Dashed lines show scale heights
    at $10^4\;\mathrm{K}$ for each of the two simulations.}
    \label{multiphase_properties}
\end{figure}
In order to compare superbubble feedback to \citet{DallaVecchia2012}, we selected
similar galaxies to the ones shown in their paper and calculated the properties
of their outflows using a similar method.  We adopt their two primary metrics,
mass outflow rate $\dot M$ and mean outflow velocity $<v_{\rm out}>$.  These two
metrics give us an idea as to both how much gas is ejected from the galaxies,
and how long that gas will take to return to the disc from the halo (if it does
return at all).

@@

\section*{Acknowledgements}
The analysis was performed using the pynbody package \\
(\texttt{https://github.com/pynbody/pynbody}, \citep{pynbody})
  We thank Mordecai-Mark Mac Low for useful
conversations regarding this paper.  The simulations were performed on the
clusters hosted on {\sc sharcnet}, part of ComputeCanada.  We greatly
appreciate the contributions of these computing allocations. James Wadsley and
Hugh Couchman thank NSERC for funding support.
\bibliographystyle{mnras}
\bibliography{library}
